---
title: "Regression Analysis"
author: "Kar"
date: '2022-06-07'
output: html_document
---

## 1 INTRODUCTION

This project will analyse the business datasets used in the book **"ESSENTIALS OF STATISTICS FOR BUSINESS AND ECONOMICS"** by David R.Anderson (University of Cincinnati), Dennis J. Sweeney (University of Cincinnati), and Thomas A. Williams (Rochester Institute of Technology).


## 2 R PACKAGES

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(cowplot)
library(kableExtra)

```

## 3 ANALYSIS

### 3.1 Transportation Schedule

To develop a better work schedules, the managers of Butler Trucking Company wants to estimate the total daily travel time for their drivers. 

There are 2 explanatory variables "miles traveled" and "number of deliveries", and 1 responding variable "travel time per hour". This analysis will find out the statistical relationship between the responding variable with these explanatory variable.

Dataset:

```{r}

driving.assignment <- c(1:10)
miles.traveled <- c(100, 50, 100, 100, 50, 80, 75, 65, 90, 90)
number.of.deliveries <- c(4, 3, 4, 2, 2, 2, 3, 4, 3, 2)
travel.time.hrs <- c(9.3, 4.8, 8.9, 6.5, 4.2, 6.2, 7.4, 6, 7.6, 6.1)

transport.df <- data.frame(driving.assignment, miles.traveled, number.of.deliveries, travel.time.hrs)

transport.df %>% kbl() %>% kable_styling(bootstrap_options = c("striped", "bordered"), full_width = F)

```

```{r}
g1.transport <- ggplot(transport.df, aes(x = miles.traveled, y = travel.time.hrs)) + geom_point()
g2.transport <- ggplot(transport.df, aes(x = number.of.deliveries, y = travel.time.hrs)) + geom_point()

plot_grid(g1.transport, g2.transport)


```

**Simple linear Regression**:

The dataset will be analysed with multiple linear regression method, but following is a simple linear regression, it is an optional step, I create it to compare with multiple linear regression on how metrics change.

```{r}
transport.lm <- lm(travel.time.hrs ~ miles.traveled, 
                   data = transport.df)

summary(transport.lm)

```
* At the 0.05 level of significance, the F-statistic is 15.83 and its corresponding p-value of 0.00408 indicates that the relationship is significant. Therefore, the null hypothesis is rejected because the p-value is less than a = 0.05. 

* The relationship between total travel time and miles is significant related. Longer travel times are associated with more miles travel. 

* With a **coefficient of determination** of R-sq = 66.4%. We see that 66.4% of the variability in travel time can be explained by the linear effect of the number of miles traveled.

* formula: 

y = 1.27 + 0.067(miles.travel)

**Miltiple Lienar regression**

```{r}
names(transport.df)

```

```{r}
transport.lm2 <- lm(travel.time.hrs ~ miles.traveled + number.of.deliveries,
                    data = transport.df)

summary(transport.lm2)

```
Both variables are statistically associated with the traveling time. 

* b1: 0.0611. It is expecting that 0.0611 hours (3.7 minutes) will increase in travel time corresponding to an increase in **1 mile** in the distance traveled when the *number of deliveries* is held constant. 

* b2: 0.923. It is expecting that 0.923 hours (55 minutes) will increase in travel time corresponding to an increase in **1 delivery** when the **number of miles** traveled is held constant.


### 3.2 Movie Theater Gross Revenue

The owner of showtime Movie Theaters, Inc, would like to estimate weekly gross revenue as a function of advertising expenditures. 

Responding variables:
* weekly.gross.rev, in the unit of $1000s

Explanatory veriables:
* Tv.ads, in the unit of $1000s  
* Newspaper.ads, in the unit of $1000s  

Historical data: 

```{r}
weekly.gross.rev <- c(96, 90, 95, 92, 95, 94, 94, 94)
tv.ads <- c(5, 2, 4, 2.5, 3, 3.5, 2.5, 3)
newpaper.ads <- c(1.5, 2, 1.5, 2.5, 3.3, 2.3, 4.2, 2.5)

movie.df <- data.frame(weekly.gross.rev, tv.ads, newpaper.ads)

movie.df %>% kbl() %>% kable_styling(bootstrap_options = c("striped", "bordered"), full_width = F)

```

```{r}
g1.movie <- ggplot(movie.df, aes(x = tv.ads, y = weekly.gross.rev)) + geom_point()
g2.movie <- ggplot(movie.df, aes(x = newpaper.ads, y = weekly.gross.rev)) + geom_point()

plot_grid(g1.movie, g2.movie)
```

Q1: Develop an estimated regression equation with the amount of tv advertising as the independent variable.

```{r}
movie.lm <- lm(weekly.gross.rev ~ tv.ads, 
               data = movie.df)

summary(movie.lm)

```
* At the 0.05 level of significance (alpha), the F test of 11.27 and the p-value of 0.015 indicates that the relationship between tvads and weekly gross revenue is significant. 

* Equation:  y = 88.637 * 1.70 (tv.ads)





